\section{Budget Justification}

 \section*{Senior/Key Personnel:}
%For each Senior/Key Person, enter the appropriate information. List personnel, salary funds, and the number of months that person will be allocated to the project. Also include a written narrative in the budget justification that fully justifies the need for requested personnel.
\begin{itemize}
\item Luke Van Roekel (10\% FTE) is the Lead PI and will serve as the project POC.  He will also mentor the LANL post-doc and provide guidance on simulation configuration and execution.  While the commitment seems small, the questions asked and addressed in this proposal are of critical importance to the E3SM Water cycle group, of which he is a co-lead.  Part of his E3SM effort will be devoted to this project as in-kind support.

\item Post-doc (50\%)  will be hired to conduct simulations with E3SM.  This postdoc will assist in the design of the new mesh and will lead the creation, spin up, and simulations with the mesh.

\end{itemize}
%List personnel, salary funds, and the number of months that person will be allocated to the project. Also include a written narrative in the budget justification that fully justifies the need for requested personnel.
%
\section*{Equipment:}
There is no specialized equipment for this project.
%
\section*{Travel:}
Approximately \$6k/year per investigator is included for two domestic trips during the year, an important cost for
the frequent interactions needed in a multi-institution efforts and to communicate scientific results to the broader community.

\section*{Materials and supplies:}
M\&S include approximately \$5k in year 1 for computing and related software for the LANL postdoc and \$5K in years 2-4 for publications.

\section*{Subcontracts:}
Approximately half of the budget will go to Samantha Siedlecki and Sulagna Ray at the University of Connecticut.  This will primarily support Co-I Ray at 100\%.  There is also small expenses included for travel (\$2K per year) and a new RAID storage in year 1 (\$3K) for processing and analyzing large datasets.  As above, sufficient travel is important for coordination and presentation of results.

\section*{Indirect costs:}
Triad National Security, LLC / Los Alamos National Laboratory (Triad/LANL) does not disclose any rates. Triad/LANL’s pricing rates are proprietary information and are generally not released externally. However, because of its contractual relationship with NNSA, LANL operations and accounting practices are fully auditable by the DOE Inspector General on a regular basis, as well as by LANL’s internal audit group.

